Towards Practical First-Order Model Counting

### 2023-08-28 paper.tex
Editing the algorithms

\usepackage{listings}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[capitalize,noabbrev]{cleveref}
\usepackage{microtype}

@@

@@

  \item Added a CLI option \texttt{--sizes} to specify the domain sizes on the
        command line.

@@

        crane, substituting the known values of preveiously calculated model

@@

@@

@@

        % Algorithm steps
        base\_cases $\leftarrow$ Set()

        \ForEach{dependency $\in$ dependencies}{
          \ForEach{elem $\in$ dependency.value}{
            \If{dependency.key.func\_name = elem.func\_name}{
              \ForEach{arg $\in$ elem.args}{
                \tcp{eg : lim is 2 for the arg (x-3)}
                lim $\leftarrow$ arg.const\_subtracted - 1 \\
                \For{l $\in$ 0 to lim}{
                  \tcp{eg : for dependency.key = f(x,y), arg = x and l = 0, add f(0, y) to base\_cases}
                  base\_cases += dependency.key.substitute\_arg(arg\_var, l)
                }
              }
            }
            \Else{
              \ForEach{arg $\in$ elem.args}{
                \tcp{eg : lim is 2 for the arg (x-3)}
                lim $\leftarrow$ arg.const\_subtracted - 1 \\
                \For{l $\in$ 0 to lim}{
                  \tcp{eg : for dependency.key = f(x,y), arg = x and l = 0, add f(0, y) to base\_cases}
                  base\_cases += dependency.key.substitute\_arg(arg, l)\\
                  \tcp{signature for f(x-1, y-2) is f(x,y)}
                  base\_cases += elem.signature.substitute\_arg(arg, l)
                }
              }
            }
          }
        }
\end{algorithm}

@@

\begin{algorithm}[t]
  \caption{Algorithm For Transforming CNF Based on Domain Sizes}\label{alg2}
  \KwIn{cnf, dom, dom\_size}
  \KwOut{transformed\_cnf, multiplier}
  removed\_predicates $\leftarrow$ Set()
  retained\_predicates $\leftarrow$ Set()
  \If{dom\_size = 0}{
    \ForEach{clause $\in$ cnf}{
      \If{dom $\in$ clause.domains}{
        removed\_predicates += clause.predicates
      }
      \Else{
        retained\_predicates += clause.predicates
        transformed\_cnf += clause
      }
    }
    removed\_predicates = removed\_predicates $\setminus$ retained\_predicates
    \ForEach{pred $\in$ removed\_predicates}{
      multiplier *= $2^{(pred.domain\_sizes.join("*"))}$
    }
  }
  \ElseIf{dom\_size = 1}{
    const $\leftarrow$ newConst()
    \ForEach{clause $\in$ cnf}{
      transformed\_clause $\leftarrow$ clause
      \ForEach{v $\in$ clause.vars | v.domain = dom}{
        transformed\_cnf $\leftarrow$ transformed\_clause.substituteVar(v, const)
      }
      transformed\_cnf += transformed\_clause
    }
  }
\end{algorithm}

>>>>

\usepackage{listings}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[capitalize,noabbrev]{cleveref}
\usepackage{microtype}
\usepackage{amsfonts}
\usepackage{mathtools}

@@

\crefname{line}{line}{lines}

\DeclareMathOperator{\Dom}{Dom}
\DeclareMathOperator{\Doms}{Doms}
\DeclareMathOperator{\Preds}{Preds}
\DeclareMathOperator{\Vars}{Vars}

@@

@@

        crane, substituting the known values of previously calculated model

@@

  \item The report has some (long) examples of formulas being transformed into
        programs perhaps suitable for supplementary material.

@@

For any dependency key, element signature, or clause $P$, argument or variable
$x$, and number or constant $t$, we shall write $P[t / x]$ for the result of
substituting $t$ for all occurrences of $x$ in $P$.

@@

  base\_cases $\gets \emptyset$\;
  \ForEach{dependency $\in$ dependencies}{
    \ForEach{elem $\in$ dependency.value}{
      \ForEach{arg $\in$ elem.args}{
        \For{l $\in$ 0 to arg.const\_subtracted - 1}{\label{line:lim}
          base\_cases += dependency.key[l / arg]\;\label{line:insert}
          \If{dependency.key.func\_name $\ne$ elem.func\_name}{
            base\_cases += elem.signature[l / arg]\;\label{line:signature}
          }
        }
      }
    }
  }
\end{algorithm}

\begin{itemize}
  \item \cref{line:lim}: eg : the limit is 2 for the arg (x-3)
  \item \cref{line:insert} eg : for dependency.key = f(x,y), arg = x and l = 0,
        add f(0, y) to base\_cases
  \item \cref{line:signature} signature for f(x-1, y-2) is f(x,y)
\end{itemize}

@@

\begin{algorithm}[t]
  \caption{Transforming Formulas Based on Domain Sizes}\label{alg2}
  \KwIn{formula $\phi$, domain $\Delta$, target domain size $n \in \{\, 0, 1 \,\}$, domain size function $|\cdot|$}
  \KwOut{formula $\phi'$, multiplier $m \in \mathbb{N}$}
  $P^{-} \gets \emptyset$; $P^{+} \gets \emptyset$; $\phi' \gets \emptyset$; m $\gets 1$\;
  \uIf{$|\Delta| = 0$}{
    \ForEach{clause $C \in \phi$}{
      \uIf{$\Delta \in \Doms(C)$}{
        $P^{-} \gets P^{-} \cup \Preds(C)$\;
      }
      \Else{
        $P^{+} \gets P^{+} \cup \Preds(C)$\;
        $\phi' \gets \phi' \cup \{\, C \,\}$\;
      }
    }
    $P^{-} \gets P^{-} \setminus P^{+}$\;
    \ForEach{predicate $P \in P^{-}$}{
      m *= $2^{(pred.domain\_sizes.join("*"))}$\;
    }
  }
  \ElseIf{$|\Delta| = 1$}{
    $c \gets$ a new constant symbol\;
    \ForEach{clause $C \in \phi$}{
      $C' \gets C$\;
      \ForEach{$v \in \Vars(C)$ with $\Dom(v) = \Delta$}{
        $C' \gets C'[c / v]$\;
      }
      $\phi' \gets \phi' \cup \{\, C' \,\}$\;
    }
  }
\end{algorithm}
% TODO: either the target domain size or the domain size function needs to go

\begin{itemize}
  \item Formulas are in CNF. Formulas are (multi) sets of clauses.
  \item $P^{-}$ --- removed predicates
  \item $P^{+}$ --- retained predicates
  \item $\phi'$ --- transformed version of $\phi$
  \item $C'$ --- transformed version of clause $C$
  \item For any clause $C$, let $\Doms(C)$, $\Preds(C)$, and $\Vars(C)$ denote
        respectively the set of domains, predicates, and variables in $C$. For
        any variable $v$, let $\Dom(v)$ denote its domain. Note that, for any
        clause $C$, we have that
        $\Doms(C) = \{\, \Dom(v) \mid v \in \Vars(C) \,\}$. Similarly, for any
        predicate $P$, let $\Doms(P)$ denote the set of domains associated with
        $P$.
\end{itemize}
